Numerous variables relating to 2016 election in 2021 US GSS^[Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis.git]

### 2022-03-19 outputs/paper/paper.Rmd

---
title: "Numerous variables relating to 2016 election in 2021 US GSS"
subtitle: "Possible factors effecting 2016 election"
author: 
  - SangWoong Lee
  - Young Suk 
thanks: "Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis.git".
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence (what was done). Second sentence(what was found). Third sentence (why this matters). Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

@@

# Data
A sense of the datasets should be communicated to the reader.
All varaiables should be throughly examined and explained.
Explain if there were similar datasets that could have been used and why they were not.
Why did we clean some variables?
what the variables look like using graphs or tables discussion of the observations.
Summary statistics should also be included

```{r}
library(ggplot2)
library(dplyr)
reduced_data %>%
  ggplot(aes(x = age, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate")

reduced_data$pres16 <- factor(reduced_data$pres16, levels = c("Clinton","Trump","Other","Did not vote"))
reduced_data %>%
  ggplot(aes(x = pres16, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate")

@@

reduced_data %>%
  ggplot(aes(x = degree, fill = factor(Family_income, levels = c("$170,000 or over","$130,000 ~ $169,999","$90,000 ~ $129,999","$60,000 ~ $89,999","$40,000 ~ $59,999","$20,000 ~ $39,999","$10,000 ~ $19,999","Under $10,000")))) +
  geom_bar() +
  labs(fill = "Family Income") +
  coord_flip()

reduced_data$Immigration <- factor(reduced_data$Immigration, levels = c("Strongly disagree","Disagree", "Neither","Agree","Strongly agree"))
reduced_data %>%
  ggplot(aes(x = Immigration, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate") +
  coord_flip()

>>>>

---
title: "Numerous variables relating to 2016 election in 2021 US GSS^[Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis.git]"
subtitle: "Possible factors effecting 2016 election"
author: 
  - SangWoong Lee
  - Young Suk
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence (what was done). Second sentence(what was found). Third sentence (why this matters). Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
library(tidyverse)
library(dplyr)
```

@@

# Data
```{r, include=FALSE, echo=FALSE}
reduced_data <- read_csv("outputs/data/prepared_gss.csv")
```
1.Conveying a sense of the dataset of interest.
2.Dicussion of the survey's methodology and its key features, strengths, weaknesses.
For instance what is the population, frame and sample.
How is the sample recruited 
what sampling approach is taken
what are some of the trade offs of this 
how is non response handled.
(What is good and bad about it

A sense of the datasets should be communicated to the reader.
All varaiables should be throughly examined and explained.
Explain if there were similar datasets that could have been used and why they were not.
Why did we clean some variables?
what the variables look like using graphs or tables discussion of the observations.
Summary statistics should also be included

```{r, echo=FALSE}
ggplot(reduced_data, aes(x = age)) +
  geom_bar(na.rm = T)

reduced_data %>%
  ggplot(aes(x = age, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate")

reduced_data$pres16 <- factor(reduced_data$pres16, levels = c("Clinton","Trump","Other","Did not vote"))

reduced_data %>%
  ggplot(aes(x = pres16, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate")

@@

reduced_data %>%
  ggplot(aes(x = degree, fill = factor(Family_income, 
                                       levels = c("$170,000 or over","$130,000 ~ $169,999","$90,000 ~ $129,999","$60,000 ~ $89,999",
                                                  "$40,000 ~ $59,999","$20,000 ~ $39,999","$10,000 ~ $19,999","Under $10,000")))) +
  geom_bar() +
  labs(fill = "Family Income") +
  coord_flip()

reduced_data$Immigration <- factor(reduced_data$Immigration, levels = c("Strongly disagree","Disagree", "Neither","Agree","Strongly agree"))

reduced_data %>%
  ggplot(aes(x = Immigration, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate") +
  coord_flip()
